---
title: "FIFA World Cup 2018 Stats"
runtime: shiny
output:
   flexdashboard::flex_dashboard:
     vertical_layout: fill
---


Visualization {data-orientation=columns}
=====================================

```{r global, include=FALSE}
library(flexdashboard)
library(plotly)
library(rvest)
library(stringr)
library(purrr)
library(dplyr)
library(tidyr)
library(ggplot2)

options(shiny.sanitize.errors = FALSE)

# Scrapping the tables
url<- read_html("https://www.mykhel.com/football/fifa-world-cup-2018-team-stats-l4/") 

tables<- html_nodes(url,'table') %>% html_table()
tables <- tables[1:8]


# Joining the tables
teams<-tables %>% reduce(left_join, by = "Team")


# Removing the % sign
teams2 <- teams %>% mutate('Pass compleated' = as.numeric( str_remove_all(`PC (%)`,"%")),
                           `Average Ball Possession` = as.numeric( str_remove_all(`Average Ball Possession`,"%")),
                           Matches = Matches.y,
                           `Goals Conceded` = `Goals Conceded.y`)

# reomving doublicated Variables
teams2 <- teams2 %>% select(-starts_with("Matches."),
                            -starts_with("Goals Conceded."),
                            -`PC (%)`,
                            -`Group Name`)
Teams<- unique(teams2$Team)



```

Column {data-width=200 .sidebar}
-----------------------------------------------------------------------

```{r}
# choose the team here
selectInput("Var3", "Choose a country to highlight",
            Teams,
            selected =Teams[10] )

# choose the variable 1 here
selectInput("Var","Choose variable to compare between countries:" , 
                  colnames(teams2),
                  selected = colnames(teams2)[31])
# choose the variable 2 here
selectInput("Var2", "Choose a sccandry variable to compare with the first variable:",
            colnames(teams2),
            selected = colnames(teams2)[32])


```
 Source: mykhel.com
 
Link to [Data source](https://www.mykhel.com/football/fifa-world-cup-2018-team-stats-l4/)

Link to [Artical](http://the42.ie/4290005)


Column {data-width=500}
-----------------------------------------------------------------------

### Overall Performance

```{r}

# Producing the main plot
 renderPlotly({
   
teams3<-teams2 %>%
  mutate(highlight = ifelse(Team == input$Var3,input$Var3,"Average Value"),
         `Passes Completed (PC)` = `Passes Completed (PC)`/100,
         `Passes Attempted (PA)` = `Passes Attempted (PA)`/100,
         `Recoveries` = Recoveries/100) %>%
  group_by(highlight) %>%
  summarise_all(.funs = mean) %>%
  select(-`Pass compleated`) %>% 
  gather(key = Variable, value = value,3:37) %>%
  arrange(desc(value))
# First plot
p1 <- teams3 %>%  ggplot(aes(x= reorder(Variable, value), y= value, fill = highlight)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(title = element_text(paste(input$Var3,"Performance Compared to\n average values in the world cup")))+
  xlab("Variable") +
  coord_flip() +
  theme_minimal()

# Build Interactivety with plotly 
plotly_build(p1)
     
})
```

Column {data-width=350}
-----------------------------------------------------------------------

### Team Position Amoung All Teams

```{r}
# Producing the Secandry plot
#  renderPlotly({
# teams2 %>% mutate(highlight = ifelse(Team == input$Var3,T,F)) %>% 
#   plot_ly(y = ~Team, x= ~get(input$Var),
#           type = 'bar', text = ~get(input$Var),
#           color = ~highlight, orientation = 'h') %>%
#   layout(title = paste0(input$Var3,"`s Position in Terms of ",input$Var),
#          xaxis = list(
#            title = input$Var),
#          yaxis = list(
#            title = "Team",
#            categoryorder = "category descending",
#            categoryarray =  ~Team),
#          showlegend  = FALSE
#          )
#   }) 

renderPlotly({
  teams2 %>% mutate(highlight = ifelse(Team == input$Var3,T,F)) %>% 
    ggplot(aes(x = reorder(Team, get(input$Var)), y=  get(input$Var), fill = highlight)) +
    geom_bar(stat = "identity") +
    theme(title = element_text(paste0(input$Var3,"`s Position in Terms of ",input$Var)),
          legend.position="none") +
    xlab(input$Var) +
    ylab("Team") +
    guides(fill=FALSE) +
    coord_flip() +
    theme_minimal()
}) 


```

### Seeking for Correlationship Between Variables

```{r}
# Producing the Secandry plot

 renderPlotly({
   teams2 %>% mutate(highlight = ifelse(Team == input$Var3,F,T)) %>% 
  plot_ly(x =~get(input$Var2), y =~get(input$Var),
          color = ~highlight, type = "scatter",hoverinfo = 'text',
        text = ~paste('</br>Team: ', Team,
                      paste("</br>",input$Var2,":"), get(input$Var2),
                      paste("</br>",input$Var,":"), get(input$Var))) %>% 
     add_lines(y = ~fitted(loess(get(input$Var) ~ get(input$Var2))),
            line = list(color = '#07A4B5'),
            name = "Line", showlegend = TRUE) %>% 
     layout(title = paste('Is there A Relationship\n Between',input$Var,'And',input$Var2,'?'),
         xaxis = list(
           title = input$Var2),
         yaxis = list(
           title = input$Var),
         showlegend  = FALSE
         )

  }) 




```

About the Dashboard
=====================================

 Article link

- AFP (2018, October 16). France defied poor stats to win 2018 World Cup, says Fifa report *the42*. Retrieved from  
http://the42.ie/4290005

 Data Source

- mykhel.COM  (2018). FIFA World Cup 2018 Team Stats, *mykhel*. Available online at: https://www.mykhel.com/football/fifa-world-cup-2018-team-stats-l4/.

 Visualization URL

https://naif-alsader.shinyapps.io/Assignment3/



